Fast, Scalable Phrase-Based SMT Decoding

### 2016-05-03 acl.2016/acl2016.tex
add reviews

The Moses, Joshua and Phrasal decoders implement multithreading, while Jane uses an external application to parallelize operation. All the multi-threaded implementations report scalability problems, either in the paper (Phrasal) or via social media (Moses\footnote{https://github.com/moses-smt/mosesdecoder/issues/39} and Joshua\footnote{https://twitter.com/ApacheJoshua/status/342022794097340416}).

>>>>

The Moses, Joshua and Phrasal decoders implement multithreading, however, they all report scalability problems, either in the paper (Phrasal) or via social media (Moses\footnote{https://github.com/moses-smt/mosesdecoder/issues/39} and Joshua\footnote{https://twitter.com/ApacheJoshua/status/342022794097340416}).

Jane and mtplz are single-threaded decoders, relying on external applications to parallelize operations. This has the advantage it is easier to parallelize processing across multiple servers, not just multiple cores. However, within one server, this method does not scale beyond a small number of cores, as we shall see.
